Income Inequality is Revealed in Torontonian Apartment Maintenance

### 2022-02-07 outputs/paper/paper.Rmd
Made slight change to the title.

---
title: "Income Inequality is revealed in Torontonian Apartment Maintenance"
author: "Olaedo Okpareke"
thanks: 'Code and data are available at: https://github.com/OlaedoOkpareke/starter_folder'
date: "`r format(Sys.time(), '%d %B %Y')`"
abstract: "Housing maintenance benefits residents as it ensures proper functioning of ammenities, maintains structural integrity, and adds value to homes. However, previous research has found that there is lower priority in maintenance for public housing apartments and lower income apartments compared to their more privileged counterparts. We use data from Open data Toronto to further analyze this by using plots and tables to break down apartment scores and other attributes by Ward and apartment type,using R [@citeR] and other packages. We find that apartments in higher income wards and privately owned apartments tend to have better evaluation scores than those in lower income wards and public housing respectively. Private apartments also have higher levels of security than social housing. This report shows the inequality in standards for housing in Toronto, as well as the need for better government accountability and housing justice, as improving the gap in aparment quality helps improve the lives of poor and marginalized people."
output:
  bookdown::pdf_document2
toc: FALSE
bibliography: references.bib
---

>>>>

---
title: "Income Inequality is Revealed in Torontonian Apartment Maintenance"
author: "Olaedo Okpareke"
thanks: 'Code and data are available at: https://github.com/OlaedoOkpareke/starter_folder'
date: "`r format(Sys.time(), '%d %B %Y')`"
abstract: "Housing maintenance benefits residents as it ensures proper functioning of ammenities, maintains structural integrity, and adds value to homes. However, previous research has found that there is lower priority in maintenance for public housing apartments and lower income apartments compared to their more privileged counterparts. We use data from Open data Toronto to further analyze this by using plots and tables to break down apartment scores and other attributes by Ward and apartment type,using R [@citeR] and other packages. We find that apartments in higher income wards and privately owned apartments tend to have better evaluation scores than those in lower income wards and public housing respectively. Private apartments also have higher levels of security than social housing. This report shows the inequality in standards for housing in Toronto, as well as the need for better government accountability and housing justice, as improving the gap in aparment quality helps improve the lives of poor and marginalized people."
output:
  bookdown::pdf_document2
toc: FALSE
bibliography: references.bib
---
